Applications of the Fresnel Integral

### 2019-03-16 draft.tex
pictures, including euler/cornu spiral.

\begin{figure}[h!]
    \centering
	\includegraphics[height=5cm]{orange.jpg} \hfill
	\includegraphics[height=5cm]{orangePeel.jpg}
	\label{f:orangePeel}
	\caption{Left: Peeling an orange in a spiral of height $1/N$.\\
		Right: The flattened peel that resembles an Euler spiral.  Photos taken from \cite{BH12}.
	}
\end{figure}
There are two standard ways of peeling an orange: either cut the skin along meridians, or cut it along a spiral. We consider here the second method, and study the shape of the spiral strip, when unfolded on a table. We derive a formula that describes the corresponding flattened-out spi- ral. Cutting the peel with progressively thinner strip widths, we obtain a sequence of increasingly long spirals. We show that, after rescaling, these spirals tends to a definite shape, known as the Eu- ler spiral. The Euler spiral has applications in many fields of science. In optics, the illumination intensity at a point behind a slit is computed from the distance between two points on the Euler spi- ral. The Euler spiral also provides optimal curva- ture for train tracks between a straight run and an upcoming bend. It is striking that it can be also obtained with an orange and a kitchen knife.

@@

\begin{itemize}\item The definition of Euler Spiral
\item The relation between Fresnel Integral and Euler Spiral
\end{itemize}

>>>>

\begin{figure}[h!]
    \centering
	\includegraphics[height=5cm]{orange.jpg} \hfill
	\includegraphics[height=5cm]{orangePeel.jpg}
	\label{f:orangePeel}
	\caption{Left: Peeling an orange in a spiral of height $1/N$.
		Right: The flattened peel that resembles an Euler spiral.  Photos taken from \cite{BH12}.
	}
\end{figure}
There are two standard ways of peeling an orange: either cut the skin along meridians, or cut it along a spiral. We consider here the second method, and study the shape of the spiral strip, when unfolded on a table. We derive a formula that describes the corresponding flattened-out spi- ral. Cutting the peel with progressively thinner strip widths, we obtain a sequence of increasingly long spirals. We show that, after rescaling, these spirals tends to a definite shape, known as the Eu- ler spiral. The Euler spiral has applications in many fields of science. In optics, the illumination intensity at a point behind a slit is computed from the distance between two points on the Euler spi- ral. The Euler spiral also provides optimal curva- ture for train tracks between a straight run and an upcoming bend. It is striking that it can be also obtained with an orange and a kitchen knife.

@@

\begin{figure}[h!]
	\centering
	\includegraphics[height=5cm]{eulerSpiral.png}
	\label{f:eulerSpiral}
	\caption{Euler spiral.  Taken from \cite[/Fresnel\_integral\#/media/File:Cornu\_Spiral.svg]{wiki}.}
\end{figure}
\begin{itemize}\item The definition of Euler Spiral
\item The relation between Fresnel Integral and Euler Spiral
\end{itemize}
